### 2014-06-10 Simluations/Figures/diagnose_consmpa.Rmd

```{r}
 ggplot(consmpa, aes(x=speed, y = Equil.pop)) + geom_line() + facet_wrap(~harvest)
```

@@

+ `h = 0.08; s = 0.24-0.28`
+ `h = 0.09; s = 0.24-0.28`
+ `h = 0.10; s = 0.14-0.16`
+ `h = 0.12; s = 0.14-0.16`

@@

```{r sim, echo=FALSE,fig.keep='none',message=FALSE,results='hide'}
setwd("/Users/efuller/Documents/Projects/Moving_fish/MovingFish/Simluations/Aspatial_fast")
source("Parameters.R")
source("Functions.R")
require(zoo)
require(plyr)
require(lattice)
require(dplyr)
require(reshape)
steps = 300   # setting number of steps over which to take equilibrium 
harvests = 0.08
speeds = seq(0.24,0.28,0.02)
MPA = "cons"
source("Figures/variable_steps.R")
```
What it looks like is that `h=0.08, s = 0.28` failed to converge. I finally killed it after 3821 generations.

>>>>

```{r}
 ggplot(consmpa, aes(x=speed, y = Equil.pop)) + geom_line() + facet_wrap(~harvest) + geom_point()
```

@@

+ `h = 0.08; s = 0.24-0.28`
+ `h = 0.09; s = 0.24-0.28`
+ `h = 0.10; s = 0.14-0.18`
+ `h = 0.12; s = 0.14-0.18`

@@

```{r sim, echo=FALSE,fig.keep='none',message=FALSE,results='hide'}
setwd("/Users/efuller/Documents/Projects/Moving_fish/MovingFish/Simluations/Aspatial_fast")
source("Parameters.R")
source("Functions.R")
require(zoo)
require(plyr)
require(lattice)
require(dplyr)
require(reshape)
steps = 300   # setting number of steps over which to take equilibrium 
harvests = seq(0,.15,0.01)
speeds = c(0.1,0.3)
MPA = "cons"
source("Figures/variable_steps.R")
```
What it looks like is that `h=0.08, s = 0.28` failed to converge. I finally killed it after 3821 generations.
